High-Dimensional Regularized Discriminant Analysis

### 2017-10-19 reports/paper-hdrda-anonymous.tex
added .tex for anonymous submission.
removed a bunch of latex commands generated by knitr -- was causing build
issues on the journal's site.

\documentclass[]{interact}

@@

\newcommand{\xbar}{\bar{\bm x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{thm}{Theorem}

\begin{document}

@@

<<knitr_setup, include=FALSE, echo=FALSE, cache=FALSE>>=
library(knitr)
# Round digits throughout document including \Sexpr statements.
# See Yihui's response here:
# http://stackoverflow.com/questions/11062497/how-to-avoid-using-round-in-every-sexpr
options(digits=3)

opts_chunk$set(fig.align='default', dev="postscript",
               message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, autodep=TRUE,
               dpi=300, fig.width=12, fig.height=12, out.width="\\linewidth")
@

<<setup>>=
setwd("..")
library(ProjectTemplate)
load.project()
@

<<munge_contaminated_sims>>=
# Contaminated Normal Sims
results_contaminated <- lapply(results_block_contaminated[[1]], function(r) {
  with(r, c(error_rates, p=p, mu=mu, contamination_prob=contamination_prob))
})
results_contaminated <- do.call(rbind.data.frame, results_contaminated)
results_contaminated <- tbl_df(results_contaminated)

results_contaminated <- results_contaminated %>%
  group_by(p, contamination_prob, mu) %>%
  summarise_each(funs(mean)) %>%
  arrange(p, contamination_prob, mu) %>%
  ungroup

results_contaminated <- results_contaminated %>%
  gather(Classifier, Error, -p, -contamination_prob, -mu) %>%
  mutate(p=factor(p)) %>%
  filter(mu == 0.5)

# Remove underscore from classifier names
levels(results_contaminated$Classifier) <- gsub("_", " ",
                                                levels(results_contaminated$Classifier))

# Maximum Standard Error for Contaminated Sims
max_sim_se <- with(results_contaminated, max(sqrt(Error * (1 - Error) / 500)))
max_sim_se <- round(max_sim_se, digits=3)
@

<<munge_microarray_results>>=
# Microarray Classification Results
results_microarray <- lapply(results[[1]], function(r) {
  with(r, c(error_rates, `data_set`=data_set))
})
results_microarray <- do.call(rbind.data.frame, results_microarray)
results_microarray <- tbl_df(results_microarray)

avg_error_microarray <- results_microarray %>%
    group_by(data_set) %>%
    summarise_each(funs(mean)) %>%
    gather(Classifier, Avg_Error, -data_set)

sd_error_microarray <- results_microarray %>%
  group_by(data_set) %>%
  summarise_each(funs(sd)) %>%
  gather(Classifier, SD_Error, -data_set)

# Microarray classification results are presented in a table
# Rows = classifier, columns = data set
# Cells = Error (SD) rounded to 3 digits
# The classifier with the minimum average error rate is in bold for each data set.

bold_latex <- function(x) {
  paste0('\\textbf{', x, '}')
}

results_microarray <- inner_join(avg_error_microarray, sd_error_microarray,
                                 by=c('data_set', 'Classifier')) %>%
  mutate(Table_Cells=sprintf('%.3f', Avg_Error),
         data_set=stringr::str_to_title(data_set),
         Classifier=gsub("_", " ", Classifier)) %>%
  group_by(data_set) %>%
  mutate(Table_Cells=ifelse(Avg_Error == min(Avg_Error), bold_latex(Table_Cells), Table_Cells),
         Table_Cells=sprintf('%s (%.3f)', Table_Cells, SD_Error)) %>%
  select(-Avg_Error, -SD_Error) %>%
  spread(data_set, Table_Cells)
@

<<munge_timing_comparisons>>=
# HDRDA vs RDA Timing Comparison Results

# Benchmarks are given in nanoseconds, which are converted to seconds
timings <- bind_rows(lapply(timing_results, as.data.frame), .id="p") %>%
  mutate(p=as.integer(p),
         expr=as.character(expr),
         Classifier=ifelse(startsWith(expr, "hdrda"), "HDRDA", "RDA"),
         Classifier=factor(Classifier),
         time=time / 1e9) %>%
  select(-expr) %>%
  filter(p %% 500 == 0) %>%
  tbl_df %>%
  group_by(p, Classifier) %>%
  mutate(wls_weights=1 / sd(time)) %>%
  ungroup

# Create DF for two facets in same plot
# First plot shows HDRDA vs RDA
# Second plot zooms in on HDRDA results
timings$Plot <- "Comparison of HDRDA and RDA"
timings_hdrda <- timings %>%
    filter(Classifier == "HDRDA") %>%
    mutate(Plot="HDRDA")
timings_combined <- bind_rows(timings, timings_hdrda)

# Build data frame to show relative timings in table
timing_ratios <- timings %>%
    group_by(p, Classifier) %>%
    summarize(median_time=median(time)) %>%
    tidyr::spread(Classifier, median_time) %>%
      mutate(ratio_time=RDA / HDRDA) %>%
      select(-HDRDA, -RDA)

timings_summary <- timings %>%
  group_by(Classifier, p) %>%
  summarize(mean_runtime=mean(time), sd_runtime=sd(time))

# RDA Mean Runtime in Minutes when p = 5000
rda_mean_time_p5000 <- timings_summary %>% filter(Classifier == "RDA", p == 5000)
rda_mean_time_p5000 <- rda_mean_time_p5000$mean_runtime / 60

# HDRDA Mean Runtime in Seconds when p = 5000
hdrda_mean_time_p5000 <- timings_summary %>% filter(Classifier == "HDRDA", p == 5000)
hdrda_mean_time_p5000 <- hdrda_mean_time_p5000$mean_runtime
@

<<bootstrap_relative_timing_comparisons>>=
ratio_means <- function(df, num_reps=1000) {
  bootstrap_reps <- replicate(n=num_reps, {
    df %>%
      group_by(Classifier) %>%
      sample_frac(size=1.0, replace=TRUE) %>%
      summarize(mean_time=mean(time)) %>%
      tidyr::spread(Classifier, mean_time) %>%
      mutate(ratio_means=RDA / HDRDA) %>%
      select(-HDRDA, -RDA)
  }, simplify=FALSE)
  bind_rows(bootstrap_reps)
}

set.seed(42)
timing_ratios_bootstrap <- timings %>%
    mutate(p=factor(p)) %>%
    group_by(p) %>%
    do(ratio_means(., num_reps=1000))

timing_bootstrap_summary <- timing_ratios_bootstrap %>%
  group_by(p) %>%
  summarize(avg_ratio=mean(ratio_means),
            lower_ci=quantile(ratio_means, probs=0.025),
            upper_ci=quantile(ratio_means, probs=0.975))
bootstrap_summary_p500 <- timing_bootstrap_summary %>%
  filter(p == "500")
bootstrap_summary_p5000 <- timing_bootstrap_summary %>%
  filter(p == "5000")

@

@@

We also provide an efficient algorithm along with pseudocode to estimate the
\emph{HDRDA} classifier's tuning parameters in a grid search via
cross-validation. Timing comparisons between our \emph{HDRDA} implementation in
the {\tt sparsediscrim} R package available on CRAN and the standard \emph{RDA}
formulation in the {\tt klaR} R package demonstrate that as the number of
features increases, the computational runtime of the \emph{HDRDA} classifier is
drastically smaller than that of \emph{RDA}. In fact, when $p = 5000$, we show
that the \emph{HDRDA} classifier is \Sexpr{bootstrap_summary_p5000$avg_ratio}
times faster on average than the \emph{RDA} classifier. In this scenario, the
\emph{HDRDA} classifier's model selection requires \Sexpr{hdrda_mean_time_p5000}
seconds on average, while that of the \emph{RDA} classifier requires
\Sexpr{rda_mean_time_p5000} minutes on average.

@@

In Figure \ref{fig:timing-results}, we plotted the runtime of the model
selections for both the \emph{HDRDA} and \emph{RDA} classifiers as a function of
$p$. We observed that the \emph{HDRDA} classifier was substantially faster than
the \emph{RDA} classifier as $p$ increased. In the left panel of Figure
\ref{fig:timing-results}, we fit a quadratic regression line to the \emph{RDA}
runtimes and a simple linear regression model to the \emph{HDRDA} runtimes.  For
improved understanding, in the right panel we repeated the same scatterplot and
linear fit with the timings restricted to the observed range of the \emph{HDRDA}
timings. Figure \ref{fig:timing-results} suggests that the usage of a matrix
inverse and determinant in the {\tt klaR} R package's discriminant function
yielded model-selection timings that exceeded linear growth in $p$. Because the
\emph{HDRDA} classifier removes inverse and determinants, it was computationally
more efficient than the \emph{RDA} classifier, especially as $p$ increased. In
fact, when $p = 5000$, the \emph{RDA} classifier required
\Sexpr{rda_mean_time_p5000} minutes on average to perform model selection, while
the \emph{HDRDA} classifier selected its optimal model in
\Sexpr{hdrda_mean_time_p5000} seconds on average. Clearly, the model selection
employed by the \emph{HDRDA} classifier is substantially faster than that of the
\emph{RDA} classifier.

We quantified the relative timing comparisons between the two classifiers by
calculating the ratio of mean timings of the \emph{RDA} classifier to the
\emph{HDRDA} classifier for each value of $p$. We employed nonparametric
bootstrapping to estimate the mean ratio along with 95\% confidence
intervals. In Figure \ref{fig:timing-comparison-bootstrap}, the bootstrap
sampling distributions for the ratio of mean timings are given. First, we
observe that the mean relative timings increased as $p$ increased. For smaller
dimensions, the relative difference in computing was sizable with the average
ratio of the mean timings equal to \Sexpr{bootstrap_summary_p500$avg_ratio} for
$p = 500$ and a 95\% confidence interval of
(\Sexpr{bootstrap_summary_p500$lower_ci},
\Sexpr{bootstrap_summary_p500$upper_ci}). Furthermore, the ratio of mean
computing times suggested that the \emph{RDA} classifier is impractical for
higher dimensions. For instance, when $p = 5000$, the ratio of mean computing
times increased to \Sexpr{bootstrap_summary_p5000$avg_ratio} with a 95\%
confidence interval of (\Sexpr{bootstrap_summary_p5000$lower_ci},
\Sexpr{bootstrap_summary_p5000$upper_ci}).

@@

We demonstrated that our \emph{HDRDA} implementation in the {\tt sparsediscrim}
R package can be used in practice with high-dimensional data sets. In our timing
comparisons, we showed that \emph{HDRDA} model selection could be employed on
data sets with $p = 5000$ in \Sexpr{hdrda_mean_time_p5000} seconds on
average. Contrarily, the \emph{RDA} classifier implemented in the {\tt klaR} R
package required \Sexpr{rda_mean_time_p5000} minutes on average to perform model
selection on data sets with $p = 5000$. Given that the \emph{RDA} classifier has
been shown to have excellent performance in the high-dimensional setting
\citep{Webb:2011vu} but is limited by its computationally intense
model-selection procedure, our work replaces the \emph{RDA} classifier for
high-dimensional data in practice. This result is reassuring because the
\emph{RDA} classifier remains widely popular in the literature. In fact,
variants of the RDA classifier have been applied to microarray data
\citep{Ching:2012fu,Li:2012ev,Tai:2007bk,Guo:2007te}, facial recognition
\citep{Zhang:2010va,Dai:2007vd,Lu:2005hq,Pima:2004vw,Lu:2003we}, handwritten
digit recognition \citep{Bouveyron:2007gx}, remote sensing
\citep{Tadjudin:1999fk}, seismic detection \citep{Anderson:2002kg}, and chemical
spectra \citep{Wu:1996us,Aeberhard:1993fp}.

@@

<<classification_results, results='asis'>>=
table_caption <- 'The average of the test error rates obtained on gene-expression data sets over 100 random training-test partitions. Standard deviations of the test error rates are given in the parentheses. The classifier with the minimum average error rate for each data set is in bold.'

xtable_out <- xtable(results_microarray,
                     caption=table_caption,
                     label='tab:microarray-results')
print(xtable_out, include.rownames=FALSE, sanitize.text.function = function(x) { x },
      scalebox='0.85') # scales the table to fit the page
@

@@

\begin{figure}
<<hdrda_contours, fig.width=8, fig.height=8, out.width='.33\\linewidth', fig.show='hold'>>=
rda_contours(lambda = 0)
rda_contours(lambda = 0.2)
rda_contours(lambda = 0.4)
rda_contours(lambda = 0.6)
rda_contours(lambda = 0.8)
rda_contours(lambda = 1)
@
\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

@@

\begin{figure}
<<timing_results, fig.width=8, fig.height=8>>=
p <- ggplot(timings_combined, aes(x=p, y=time, color=Classifier))
p <- p + geom_point() + geom_jitter(width=140, height=0) + facet_wrap(~ Plot, scales="free_y")
p <- p + geom_smooth(method="lm", formula=y ~ poly(x, 2), se=FALSE)
p <- p + scale_color_manual(values=c("#D55E00", "#0072B2"))
p <- p + xlab("Number of Features") + ylab("Model Selection Time (seconds)")
p + theme_bw()
@
\caption{Timing comparisons (in seconds) between HDRDA and RDA classifiers.}
\label{fig:timing-results}
\end{figure}

@@

\begin{figure}
<<relative_timings, fig.width=8, fig.height=8>>=
p <- ggplot(timing_ratios_bootstrap, aes(ratio_means, fill=p))
p <- p + geom_histogram() + facet_wrap(~ p, scale="free_x", labeller="label_both")
p <- p + xlab("Ratio of Mean RDA Runtime to Mean HDRDA Runtime") + ylab("Bootstrap Replications")
p + theme_bw()
@
\caption{Distribution of ratios of mean \emph{RDA} runtime to mean \emph{HDRDA}
  runtime across 1000 bootstrap replications.}
\label{fig:timing-comparison-bootstrap}
\end{figure}

@@

\begin{figure}
<<sim_results, fig.width=8, fig.height=8>>=
p <- ggplot(results_contaminated, aes(x=contamination_prob, y=Error))
p <- p + geom_line(aes(color=Classifier, linetype=Classifier), size=0.65)
p <- p + facet_wrap(~ p, labeller = "label_both")
p <- p + xlab("Contamination Probability") + ylab("Average Error Rate")
p + theme_bw()
@
\caption{Average classification error rates as a function of the contamination
  probability $\epsilon$. Approximate standard errors were no greater than
  \Sexpr{max_sim_se}.}
\label{fig:sim-results}
\end{figure}

@@

\begin{figure}
<<sim_results_by_p, fig.width=8, fig.height=8>>=
p2 <- results_contaminated %>%
  mutate(p=as.numeric(as.character(p)),
         contamination_prob=round(contamination_prob, digits=2)) %>%
    filter(contamination_prob %in% c(0.0, 0.1, 0.2, 0.3, 0.4, 0.5)) %>%
    rename(`Contamination Probability`=contamination_prob) %>%
      ggplot(., aes(x=p, y=Error))
p2 <- p2 + geom_line(aes(color=Classifier, linetype=Classifier), size=0.65)
p2 <- p2 + facet_wrap(~ `Contamination Probability`, labeller="label_both")
p2 <- p2 + xlab("Number of Features") + ylab("Average Error Rate")
p2 + theme_bw()
@
\caption{Average classification error rates as a function of the number of
  features $p$. Approximate standard errors were no greater than
  \Sexpr{max_sim_se}.}
\label{fig:sim-results-by-p}
\end{figure}

>>>>

\documentclass[]{interact}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{alltt}

@@

\newcommand{\xbar}{\bar{\bm x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{thm}{Theorem}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

@@

We also provide an efficient algorithm along with pseudocode to estimate the
\emph{HDRDA} classifier's tuning parameters in a grid search via
cross-validation. Timing comparisons between our \emph{HDRDA} implementation in
the {\tt sparsediscrim} R package available on CRAN and the standard \emph{RDA}
formulation in the {\tt klaR} R package demonstrate that as the number of
features increases, the computational runtime of the \emph{HDRDA} classifier is
drastically smaller than that of \emph{RDA}. In fact, when $p = 5000$, we show
that the \emph{HDRDA} classifier is 502.786
times faster on average than the \emph{RDA} classifier. In this scenario, the
\emph{HDRDA} classifier's model selection requires 2.979
seconds on average, while that of the \emph{RDA} classifier requires
24.933 minutes on average.

@@

In Figure \ref{fig:timing-results}, we plotted the runtime of the model
selections for both the \emph{HDRDA} and \emph{RDA} classifiers as a function of
$p$. We observed that the \emph{HDRDA} classifier was substantially faster than
the \emph{RDA} classifier as $p$ increased. In the left panel of Figure
\ref{fig:timing-results}, we fit a quadratic regression line to the \emph{RDA}
runtimes and a simple linear regression model to the \emph{HDRDA} runtimes.  For
improved understanding, in the right panel we repeated the same scatterplot and
linear fit with the timings restricted to the observed range of the \emph{HDRDA}
timings. Figure \ref{fig:timing-results} suggests that the usage of a matrix
inverse and determinant in the {\tt klaR} R package's discriminant function
yielded model-selection timings that exceeded linear growth in $p$. Because the
\emph{HDRDA} classifier removes inverse and determinants, it was computationally
more efficient than the \emph{RDA} classifier, especially as $p$ increased. In
fact, when $p = 5000$, the \emph{RDA} classifier required
24.933 minutes on average to perform model selection, while
the \emph{HDRDA} classifier selected its optimal model in
2.979 seconds on average. Clearly, the model selection
employed by the \emph{HDRDA} classifier is substantially faster than that of the
\emph{RDA} classifier.

We quantified the relative timing comparisons between the two classifiers by
calculating the ratio of mean timings of the \emph{RDA} classifier to the
\emph{HDRDA} classifier for each value of $p$. We employed nonparametric
bootstrapping to estimate the mean ratio along with 95\% confidence
intervals. In Figure \ref{fig:timing-comparison-bootstrap}, the bootstrap
sampling distributions for the ratio of mean timings are given. First, we
observe that the mean relative timings increased as $p$ increased. For smaller
dimensions, the relative difference in computing was sizable with the average
ratio of the mean timings equal to 14.513 for
$p = 500$ and a 95\% confidence interval of
(14.191,
14.855). Furthermore, the ratio of mean
computing times suggested that the \emph{RDA} classifier is impractical for
higher dimensions. For instance, when $p = 5000$, the ratio of mean computing
times increased to 502.786 with a 95\%
confidence interval of (462.863,
546.396).

@@

We demonstrated that our \emph{HDRDA} implementation in the {\tt sparsediscrim}
R package can be used in practice with high-dimensional data sets. In our timing
comparisons, we showed that \emph{HDRDA} model selection could be employed on
data sets with $p = 5000$ in 2.979 seconds on
average. Contrarily, the \emph{RDA} classifier implemented in the {\tt klaR} R
package required 24.933 minutes on average to perform model
selection on data sets with $p = 5000$. Given that the \emph{RDA} classifier has
been shown to have excellent performance in the high-dimensional setting
\citep{Webb:2011vu} but is limited by its computationally intense
model-selection procedure, our work replaces the \emph{RDA} classifier for
high-dimensional data in practice. This result is reassuring because the
\emph{RDA} classifier remains widely popular in the literature. In fact,
variants of the RDA classifier have been applied to microarray data
\citep{Ching:2012fu,Li:2012ev,Tai:2007bk,Guo:2007te}, facial recognition
\citep{Zhang:2010va,Dai:2007vd,Lu:2005hq,Pima:2004vw,Lu:2003we}, handwritten
digit recognition \citep{Bouveyron:2007gx}, remote sensing
\citep{Tadjudin:1999fk}, seismic detection \citep{Anderson:2002kg}, and chemical
spectra \citep{Wu:1996us,Aeberhard:1993fp}.

@@

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Oct 16 21:24:13 2017
\begin{table}[ht]
\centering
\scalebox{0.85}{
\begin{tabular}{lllllll}
  \hline
Classifier & Chiaretti & Chowdary & Nakayama & Shipp & Singh & Tian \\ 
  \hline
Guo & \textbf{0.111} (0.044) & 0.056 (0.051) & 0.208 (0.061) & 0.086 (0.063) & \textbf{0.089} (0.055) & 0.268 (0.082) \\ 
  HDRDA Convex & 0.115 (0.044) & 0.035 (0.026) & \textbf{0.208} (0.066) & 0.073 (0.057) & 0.111 (0.059) & 0.229 (0.049) \\ 
  HDRDA Ridge & 0.118 (0.050) & \textbf{0.033} (0.022) & 0.208 (0.070) & \textbf{0.072} (0.065) & 0.099 (0.046) & 0.225 (0.050) \\ 
  Pang & 0.663 (0.062) & 0.197 (0.091) & 0.227 (0.062) & 0.192 (0.091) & 0.221 (0.095) & 0.267 (0.054) \\ 
  Random Forest & 0.124 (0.053) & 0.045 (0.028) & 0.232 (0.063) & 0.135 (0.078) & 0.093 (0.045) & \textbf{0.206} (0.044) \\ 
  Tong & 0.195 (0.068) & 0.197 (0.091) & 0.227 (0.062) & 0.192 (0.091) & 0.221 (0.095) & 0.267 (0.054) \\ 
  Witten & 0.194 (0.068) & 0.197 (0.091) & 0.232 (0.068) & 0.193 (0.092) & 0.221 (0.095) & 0.264 (0.053) \\ 
   \hline
\end{tabular}
}
\caption{The average of the test error rates obtained on gene-expression data sets over 100 random training-test partitions. Standard deviations of the test error rates are given in the parentheses. The classifier with the minimum average error rate for each data set is in bold.} 
\label{tab:microarray-results}
\end{table}

@@

\begin{figure}
\includegraphics[width=.33\linewidth]{figure/hdrda_contours-1} 
\includegraphics[width=.33\linewidth]{figure/hdrda_contours-2} 
\includegraphics[width=.33\linewidth]{figure/hdrda_contours-3} 
\includegraphics[width=.33\linewidth]{figure/hdrda_contours-4} 
\includegraphics[width=.33\linewidth]{figure/hdrda_contours-5} 
\includegraphics[width=.33\linewidth]{figure/hdrda_contours-6}

\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figure/timing_results-1}
\caption{Timing comparisons (in seconds) between HDRDA and RDA classifiers.}
\label{fig:timing-results}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figure/relative_timings-1}
\caption{Distribution of ratios of mean \emph{RDA} runtime to mean \emph{HDRDA}
  runtime across 1000 bootstrap replications.}
\label{fig:timing-comparison-bootstrap}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figure/sim_results-1} 
\caption{Average classification error rates as a function of the contamination
  probability $\epsilon$. Approximate standard errors were no greater than
  0.022.}
\label{fig:sim-results}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figure/sim_results_by_p-1} 
\caption{Average classification error rates as a function of the number of
  features $p$. Approximate standard errors were no greater than
  0.022.}
\label{fig:sim-results-by-p}
\end{figure}
